Real-time resolution of short-read assembly graph using ONT long reads

### 2020-10-26 paper_clean.tex
last edit

Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.

@@

Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library. With all of the data sets tested, \unicycler required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
$\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level. As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies with lower N50 compared to the other hybrid assemblers. This behaviour was clearly reflected in the last, also the most challenging task of assembly \emph{S.~dysenteriae}.

@@

There was high similarity between final contigs generated by two assemblers on all of these datasets.
For the \emph{Citrobacter freundii}  dataset, they share the same number of circular  sequences, including the chromosomal and other six replicons contigs in the , with only 48 nucleotides  difference in the length of the main chromosome. 
Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
Both assemblers had $14.5$Kbp of unfinished sequences split amongst 3 linear contigs from \unicycler{} and 2 for \npgraph{}.

>>>>

Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
The nanopore read depth for each data set is approximately 65-fold coverage even though much less data were needed to generate these final results by the aforementioned hybrid methods.

@@

Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library. With all of the data sets tested, \unicycler{} required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
$\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level. As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies with lower N50 compared to the other hybrid assemblers. This behaviour was clearly reflected in the last, also the most challenging task of assembly \emph{S.~dysenteriae}.

@@

There was high similarity between final contigs generated by two assemblers on all of these datasets.
For the \emph{Citrobacter freundii}  dataset, they share the same number of circular  sequences, including the chromosomal and other six replicons contigs in the , with only 48 nucleotides  difference in the length of the main chromosome. 
Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2$Kbp of length as ColRNAI plasmid.
The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
Both assemblers had $14.5$Kbp of unfinished sequences split amongst 3 linear contigs from \unicycler{} and 2 for \npgraph{}.

### 2020-10-26 paper_edit.tex
last edit

Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
The nanopore read depth for each data set is approximately 65-fold coverage even though much less data were needed to generate these final results by the aforementioned hybrid methods.

@@

Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library. With all of the data sets tested, \unicycler{} required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
$\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level. As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies with lower N50 compared to the other hybrid assemblers. This behaviour was clearly reflected in the last, also the most challenging task of assembly \emph{S.~dysenteriae}.

@@

There was high similarity between final contigs generated by two assemblers on all of these datasets.
For the \emph{Citrobacter freundii}  dataset, they share the same number of circular  sequences, including the chromosomal and other six replicons contigs in the , with only 48 nucleotides  difference in the length of the main chromosome. 
Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2$Kbp of length as ColRNAI plasmid.
The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
Both assemblers had $14.5$Kbp of unfinished sequences split amongst 3 linear contigs from \unicycler{} and 2 for \npgraph{}.

>>>>

Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197. \review{The nanopore read depth for each data set is approximately 65-fold coverage even though much less data were needed to generate these final results by the aforementioned hybrid methods.}

@@

Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library. With all of the data sets tested, \review{\unicycler{} required} the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
$\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level. As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies with lower N50 compared to the other hybrid assemblers. This behaviour was clearly reflected in the last, also the most challenging task of assembly \emph{S.~dysenteriae}.

@@

There was high similarity between final contigs generated by two assemblers on all of these datasets.
For the \emph{Citrobacter freundii}  dataset, they share the same number of circular  sequences, including the chromosomal and other six replicons contigs in the , with only 48 nucleotides  difference in the length of the main chromosome. 
Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2$\review{Kbp} of length as ColRNAI plasmid.
The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
Both assemblers had $14.5$Kbp of unfinished sequences split amongst 3 linear contigs from \unicycler{} and 2 for \npgraph{}.
